The title

### 2018-04-25 writeup.Rmd
added link visualization

>>>>

```{r stimuli, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3, fig.height=1, set.cap.width=T, num.cols.cap=1,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
cards_img <- jpeg::readJPEG("writeup_files/link-visualization.jpg")
grid::grid.raster(cards_img)
```
